Anony\emph{mice}d shareable data: Using \emph{mice} to create and analyze multiply imputed synthetic data sets

### 2021-10-05 manuscript/Manuscript.Rmd
contribution dagger updated

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
author:
  - name: Thom Volker
    affil: 1,*
    orcid: 0000-0002-2408-7820
  - name: Gerko Vink
    affil: 1, \dagger
    orcid: 0000-0001-9767-1924
affiliation:
  - num: 1
    address: |
      Utrecht University - 
      Department of Methodology and Statistics
      Padualaan 14, 3584CH Utrecht, the Netherlands
# firstnote to eighthnote
firstnote: |
  These authors contributed equally to this work.
correspondence: |
  t.b.volker@uu.nl.
journal: psych
type: article
status: submit
bibliography: synth.bib
appendix: appendix.tex
abstract: |
  Synthetic data sets can greatly improve the dissemination of data 
  and further analysis of private data. Generating and analyzing synthetic data 
  sets is straightforward, yet adopting a synthetic data analysis pipeline is 
  often ignored by applied researchers. We outline a simple procedure for 
  generating and alayzing synthetic data sets with `mice` in `R`. We demonstrate 
  in simulation that the analysis results obtained on synthetic data 
  obtained with `mice` yields unbiased and valid inferences, and leads to synthetic 
  records that cannot be distinguished from the true data records. The ease of use 
  when synthesizing data with `mice`, together with the validity of inferences 
  obtained through this procedure opens up a wealth of possibilities for data 
  dissemination and further research of initially private data. 
keywords: |
  mice; imputation; synthetic data.
acknowledgement: |
  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
  simulation study on an independent data set. 
authorcontributions: |
  The authors contributed equally to this work.
conflictsofinterest: |
  The authors declare no conflict of interest. 
sampleavailability: |
  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
output: rticles::mdpi_article
---

>>>>

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
author:
  - name: Thom Volker
    affil: 1,*, \dagger
    orcid: 0000-0002-2408-7820
  - name: Gerko Vink
    affil: 1, \dagger
    orcid: 0000-0001-9767-1924
affiliation:
  - num: 1
    address: |
      Utrecht University - 
      Department of Methodology and Statistics. 
      Padualaan 14. 3584CH Utrecht, the Netherlands
# firstnote to eighthnote
firstnote: |
  These authors contributed equally to this work.
correspondence: |
  t.b.volker@uu.nl.
journal: psych
type: article
status: submit
bibliography: synth.bib
appendix: appendix.tex
abstract: |
  Synthetic data sets can greatly improve the dissemination of data 
  and further analysis of private data. Generating and analyzing synthetic data 
  sets is straightforward, yet adopting a synthetic data analysis pipeline is 
  often ignored by applied researchers. We outline a simple procedure for 
  generating and alayzing synthetic data sets with `mice` in `R`. We demonstrate 
  in simulation that the analysis results obtained on synthetic data 
  obtained with `mice` yields unbiased and valid inferences, and leads to synthetic 
  records that cannot be distinguished from the true data records. The ease of use 
  when synthesizing data with `mice`, together with the validity of inferences 
  obtained through this procedure opens up a wealth of possibilities for data 
  dissemination and further research of initially private data. 
keywords: |
  mice; imputation; synthetic data.
acknowledgement: |
  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
  simulation study on an independent data set. 
authorcontributions: |
  The authors contributed equally to this work.
conflictsofinterest: |
  The authors declare no conflict of interest. 
sampleavailability: |
  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
output: rticles::mdpi_article
---

### 2021-10-05 manuscript/Manuscript.tex
contribution dagger updated

% Authors, for the paper (add full first names)
\Author{Thom
Volker$^{1,*}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
Vink$^{1,
\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Utrecht University - Department of Methodology and
Statistics Padualaan 14, 3584CH Utrecht, the Netherlands; \\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:t.b.volker@uu.nl}{\nolinkurl{t.b.volker@uu.nl}}.}

>>>>

% Authors, for the paper (add full first names)
\Author{Thom Volker$^{1,*,
\dagger}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
Vink$^{1,
\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Utrecht University - Department of Methodology and
Statistics. Padualaan 14. 3584CH Utrecht, the Netherlands; \\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:t.b.volker@uu.nl}{\nolinkurl{t.b.volker@uu.nl}}.}
